\LARGE \bf Imposing a Weight Norm Constraint for Neuro–Adaptive Control

### 2025-03-24 manuscript.tex
table left align
school to department

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}}%
}

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{c c c c c }
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass of $p\textsubscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_p$  & Length of $p\textsubscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
    \hline
    ${l_c}_p$ & COM of $p\textsubscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_p$   & Viscous coef. of $p\textsubscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    ${f_c}_p$  & Friction coef. of $p\textsubscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

>>>>

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the Department of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}}%
}

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{c m{11em} c c c }
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass of $p\textsubscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_p$  & Length of $p\textsubscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
    \hline
    ${l_c}_p$ & COM of $p\textsubscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_p$   & Viscous coef. of $p\textsubscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    ${f_c}_p$  & Friction coef. of $p\textsubscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}
